---
title: "WoS API Workflow"
author: "Jill MacKay"
date: "6 December 2017"
output:
    html_document:
    keep_md: true
    theme: spacelab
    highlight: haddock
    toc: true 
    toc_float: true
    toc_depth: 3
---

# WoS API
Web of Science Web Services API by [Juba](https://github.com/juba/rwos) allows for a much smoother workflow, although you get less data in return. 

# Important Caveat
The `rwos` package is still under development (report any issues to [Juba](https://github.com/juba/rwos). You may not receive the exact same search results from this code as you would a Web of Science search)

# R Environment
At present (December, 2017) you need to install `rwos` directly from github. 
```{r eval=FALSE}
require(devtools)
library(devtools)
install_github("juba/rwos")
```

```{r}
library(rwos)

# Remember any of the below packages can be installed with "install.packages("package.name")" if you don't have them
library(tidyverse)
library(stringr)
library(knitr)
library(tibble)
library(wesanderson)
library(tm)
library(wordcloud)
library(textstem)
```

# Reading Data from WoS
## Authenticate the WoS Service
The first step is to authenticate the WoS server. You need to be using an IP address with WoS access, e.g. a university computer or a VPN connection.
```{r}
sid <- wos_authenticate()
```

## Search WoS 
Next you want to run a search and save the output of that search accordingly. 

```{r}
search.lecturecapture <- wos_search(sid, 'TO=("lecture capture")  OR TO=("lecture recording")')
pubs.lecturecapture <- wos_retrieve_all(search.lecturecapture)
```
### Current Unsolved Issue
The `wos_search` function is not giving me the exact same results as the WoS interface does (156 records vs 198) - check between the two and find out what's missing. 

## Check Results
```{r}
summary(pubs.lecturecapture)
```

### To Do
Change classes of data to categoricals (maybe with a `parse` command)



