---
title: "WoS API Workflow"
author: "Jill MacKay"
date: "04 September 2019"
output:
    html_document:
    keep_md: true
    theme: spacelab
    highlight: haddock
    toc: true 
    toc_float: true
    toc_depth: 3
---

# WoS API
Web of Science Web Services API by [Juba](https://github.com/juba/rwos) allows for a much smoother workflow, although you get less data in return. 

# Important Caveat
The `rwos` package is still under development (report any issues to [Juba](https://github.com/juba/rwos). You may not receive the exact same search results from this code as you would a Web of Science search)

# R Environment
At present (September, 2019) you need to install `rwos` directly from github. 
```{r eval=FALSE}
require(devtools)
library(devtools)
install_github("juba/rwos")
```

```{r}
library(rwos)

# Remember any of the below packages can be installed with "install.packages("package.name")" if you don't have them
library(tidyverse)
library(knitr)
library(wesanderson)
library(tidytext)
library(wordcloud)
library(textstem)

# and then for the pretty colours
library(wesanderson)
```

# Reading Data from WoS
## Authenticate the WoS Service
The first step is to authenticate the WoS server. You need to be using an IP address with WoS access, e.g. a university computer or a VPN connection.
```{r}
sid <- wos_authenticate()
```

## Search WoS 
Next you want to run a search and save the output of that search accordingly. 

```{r}
search.lecturecapture <- 
  wos_search(sid, 'TO=("lecture capture")  OR TO=("lecture recording")')

pubs.lecturecapture <- wos_retrieve_all(search.lecturecapture)
```
### Current Unsolved Issue
The `wos_search` function is not giving me the exact same results as the WoS interface does (156 records vs 242) - check between the two and find out what's missing. 

## Check Results
```{r}
pubs.lecturecapture <- 
  pubs.lecturecapture %>%
  mutate (uid = as.factor(uid),
          journal = as.factor(journal),
          issue = as.factor(issue),
          volume = as.factor (volume),
          year = as.numeric (year),
          doi = as.factor(doi),
          article_no = as.factor(article_no),
          isi_id = as.factor(isi_id),
          issn = as.factor(issn),
          isbn= as.factor(isbn))
summary(pubs.lecturecapture)
```


# Quick Visualisations
## Publications by Time
```{r}
pubs.byyear <- 
  ggplot (data = pubs.lecturecapture, 
          aes(x = year, fill=..count..)) + 
  geom_histogram(binwidth = 1) + 
  labs (title = "Lecture Recoding Publications by Year", 
        x = "Publication Year") + 
  theme_bw() + 
  scale_fill_gradientn(colors = wes_palette("Royal1"))  + 
  theme(axis.text.x = element_text(angle = 90), 
        panel.grid = element_blank()) + 
  scale_x_continuous(breaks = seq(1999,2019,1))
# Remember to check these x label breaks match with the min, max values of the dataset!

pubs.byyear
```


## What Are People Writing About?
### Visualise KeyWords
```{r}

mystops <- tibble(word = c("lecture", "record", "capture"),
                  lexicon = c("my", "my", "my")) 

mystops <- rbind(mystops, stop_words)

tidy_keywords <- 
  pubs.lecturecapture %>% 
  unnest_tokens(word, keywords, token = "words") %>% 
  mutate(word = lemmatize_strings(word)) %>% 
  anti_join(mystops) 



tidy_keywords %>% 
  count(word) %>% 
  with(wordcloud(words = word, 
                 freq = n, 
                 random.order = FALSE, 
                 max.words = 50,
                 random.color = FALSE, 
                 rot.per = 0, 
                 use.r.layout = FALSE, 
                 colors = wes_palette("Royal1")))



```

### Visualise Titles
```{r}
tidy_titles <- 
  pubs.lecturecapture %>% 
  unnest_tokens(word, title, token = "words") %>% 
  mutate(word = lemmatize_strings(word)) %>% 
  anti_join(mystops) 



tidy_titles %>% 
  count(word) %>% 
  with(wordcloud(words = word, 
                 freq = n, 
                 random.order = FALSE, 
                 max.words = 50,
                 random.color = FALSE, 
                 rot.per = 0, 
                 use.r.layout = FALSE, 
                 colors = wes_palette("Royal1")))

```











# Current Unsolved Problem 
The journal field is too detailed - how do we filter this better?


## Publications by Source
```{r}

by.journal <- 
          pubs.lecturecapture %>%
          filter(journal !="") %>%
          group_by(journal) 

by.journal <- within(by.journal, 
                   journal <- factor(journal, 
                                      levels=names(sort(table(journal), 
                                                        decreasing=TRUE))))


pubs.bysource <- ggplot (data = by.journal, aes(x = journal, fill=..count..)) + 
  geom_bar() + 
  labs (title = "Lecture Recoding Publications by Source", x = "Source Name", y = "N Publications") + 
  theme_bw() + scale_fill_gradientn(colors = wes_palette("Royal1"))  + 
  theme(axis.text.x = element_text(angle = 90), panel.grid = element_blank()) 
 
#Again - check the scaling of the y axis by the summary of the data
pubs.bysource
```

